### 2016-08-25 Results/TurkExp1WriteUp.Rnw
ks test for equality of distributions of time taken to respond

We next investigate the length of time that users' took to respond to each lineup. The minimum was 3.762 seconds and the maximum was 578.8 seconds (nearly 10 minutes). The median was 13.01 seconds and the mean was 20.32 seconds.

<<time_plot, echo=FALSE>>=
#qplot(x = res2$time, binwidth = 2)
ggplot(data = res2, aes(x = conf_level, y = time)) + geom_boxplot() + coord_flip()
ggplot(data = res2, aes(x = lineup_name, y = time)) + 
  geom_boxplot() + 
#  facet_wrap(~conf_level) + 
  coord_flip() + 
  theme_bw() + 
  labs(x = "Time (in seconds)", y = "Lineup Name")
@

>>>>

We next investigate the length of time that users' took to respond to each lineup. The minimum was 3.762 seconds and the maximum was 578.8 seconds (nearly 10 minutes). The median was 13.01 seconds and the mean was 20.32 seconds. First, a 2-sample Kolmogorov-Smirnov test for equality of distribution was done to see if the distribution of times for correct plots chosen is the same as the distribution of times for incorrect plots chosen. This two-sided test resulted in a $p$-value of 1, so there is no evidence that the distribution of times is different whether or not the response was correct.

<<time_plot, echo=FALSE>>=
#qplot(x = res2$time, binwidth = 2)
ggplot(data = res2, aes(x = conf_level, y = time)) + geom_boxplot() + coord_flip()
ggplot(data = res2, aes(x = correct, y = time)) + geom_boxplot() + coord_flip() + theme_bw()
ggplot(data = res2, aes(x = time)) + geom_histogram(binwidth = 5, fill ='white', color = 'black') + facet_wrap(~correct, nrow = 2)
ggplot(data = res2, aes(x = lineup_name, y = time)) + 
  geom_boxplot() + 
#  facet_wrap(~conf_level) + 
  coord_flip() + 
  theme_bw() + 
  labs(x = "Time (in seconds)", y = "Lineup Name")
# 2-sample kolmogorov-smirnov test for equality of distributions
# ks.test(x = summary(res2$time[res2$correct]), y = summary(res2$time[!res2$correct]))
# fail to reject null
@
